---
title: "ETC5521 Assignment 1"
subtitle: "Your title"
team: brolga
author:
  - Dilinie Seimon
  - Diyao Chen
date: "`r Sys.Date()`"
output: 
  html_document
---

```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library("tidyverse")
library("readr")
library("kableExtra")
```

[This assignment is for ETC5521 Assignment 1 by Team `r rmarkdown::metadata$team` comprising of `r knitr::combine_words(rmarkdown::metadata$author)`.]{style="color:#006DAE;"}

```{r retreiving-and-saving-data-files, eval=FALSE}
write_csv(readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/critic.tsv'), "Data/critics.csv")
write_csv(readr::read_tsv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/user_reviews.tsv'), "Data/user-reviews.csv") 
write_csv(readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/items.csv'), "Data/items.csv")
write_csv(readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/villagers.csv'), "Data/villagers.csv")
```

```{r reading-in-data}
critics <- read_csv("Data/critics.csv")
user_reviews <- read_csv("Data/user-reviews.csv")
items <- read_csv("Data/items.csv")
villagers <- read_csv("Data/villagers.csv")
```


# Introduction and motivation

[FILL] Give the bigger picture of the data, and inspire the reader to learn more about the problem by reading your analysis. 

Research findings  
- Animal Crossing New Horizons was released worldwide on 20 Mar 2020

Potential Questions  
- What do players and critics think of the game?  
- An analysis of the personalities of the villagers based on their demographics.  
- An analysis of the items and how to maximize profit by buying and selling them.  

# Data description

The dataset used for this analysis was retreived from [TidyTuesday](https://github.com/rfordatascience/tidytuesday); a project aimed at allowing individuals to practice their data wrangling and visualization skills through the use of real-world data sets.

The retreived dataset consisted of four sub-datasets -  collected from their original sources, wrangled and put into tidy form. Each of the four sub-datasets are detailed below.

```{r}
data_dict <- function(df, desc = c()){
  return(data.frame(
    "Variable" = names(df),
    "Description" = desc, 
    check.names = FALSE, row.names = NULL
  ) %>%
    kable() %>%
    kable_styling(bootstrap_options = c("striped")))
}
```

```{r}
data_dict(user_reviews, c("Raw score(0-10) given, 0-lowest and 10-highest","User name of the reviewer","Raw text of the review","Date the review was published"))
```

# Analysis and findings

[FILL] Should include at least one plot or numerical summary for each of your questions, that helps the reader arrive at an answer. You should also write paragraphs describing the methods, summaries and findings. 

# References
